### 2019-02-18 sections/intuition.tex
simplify sentence
tasks are driven by user input

This section gives an overview of the core concepts of tasks in task oriented
programming (\TOP).

@@

The evaluation of tasks is driven by input events from users. When the system
receives a valid event, it is applied to the current task, which results in a
new task. This gives rise to communication with the users of the system.

In \TOPHAT, this communication with the environment is represented by editors,
which are denoted by a box symbol.
A task of the form $\Edit v$, where $v$ is of type $\tau$, can receive a change
event with a value of type $\tau$ and additionally the special event $\Empty$
that empties the editor.
There are no external output events, instead the new task can be observed, as
described in the next section.
% However, the environment can always inspect the current value of an editor.

Editors have no notion of continuation. Their sole purpose is to facilitate
interact with the user, retaining the last value that has been sent to them.
%
Since editors can be observed in for example a user interface, they can be used
for both input and output. An empty editor is most commonly interpreted as a
prompt to input data, while a filled editor can be seen either as outputting its
value, or as an input that comes with a default or current value.

>>>>

This section gives an overview of the core concepts of task oriented programming (\TOP).

@@

Input events drive evaluation of tasks.
When the system receives a valid event, it applies the event to the current task, which results in a new task.
In this way the system communicates with the environment.

In \TOPHAT, editors are the basic method of communication with the environment.
There are different editors, denoted by different box symbols.
An editor of the form $\Edit v$, where $v$ is of type $\tau$, reacts to two kinds of events:
First, change events $v$ with a value of type $\tau$ and second, clear events $\Empty$ which empty the editor.

The sole purpose of editors is to interact with the user by retaining the last value that has been sent to them.
There are no output events.
As values of editors can be observed, for example by a user interface, editors serve as facilities for both input and output.
An empty editor $\Enter \tau$ stands for a prompt to input data, while a filled editor can be seen either as outputting its value, or as an input that comes with a default value.
